How to compute the fusion product of MV cycles in type A

### 2021-04-12 draft.tex
Corrected typo in g(A) example.
fixed typo and completed check of eqs 3

For $ s \ne 0$, we see that the equalities in $ z(s) $ reproduce the permutation $ p$, that $ r = 2 $, and that
\begin{equation} 
    \label{eq:rcols}
\begin{split}
        r_{z(s), 1}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda' \\
        r_{z(s), 2}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda'' \,. 
\end{split}
\end{equation}
On the other hand, for $z(0)$, we get that $ r = 1$ and that 
\begin{equation} \label{eq:rcol2}
r_{z(0),1}(i) = r(i) = n -  N - 
     \#\text{~boxes in first $i$ columns of }\lambda\,. 
\end{equation}
\jcom{Someone should check that I chose the notation correctly to make this work out.}

\acom{What do we mean by equalities in $z(s)$ reproduce $p$? I thought $z(s)$ was defined by $p$. Also, $r_{z(s),1}(i) = N- r(p(k_1)) + r(p(k_1 + i)) = N - (N-\#\text{boxes in first }p(k_1)\text{ cols} + \cdots)\ne $~\Cref{eq:rcols}. We want to apply $p$ to $\{1,\dots,i\}$ and not just $i$. I guess we could clarify/declare that $r(p(i)) = N - \#$ boxes in columns $p(1),\dots,p(i)$.}

@@

    In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
    % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
    In pictures, and by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
             & 1 & & & & & \\
             &  & 1 & & & & \\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
              &  & &  & 1 & & \\
              A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
             A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
             A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
        \end{BMAT}
        \right]\,. 
    \]
    % 
     To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
    of polynomials 
    $ g(A) = \left( g(A)_{ij} \right)$ in $ M_m(\CC[t]) $ as follows.
    \begin{equation}
        \label{eq:mvyofa}
        g(A)_{ij} = 
    \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j \\
            % \text{ if $ i = j$} \\
            - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j
        %  \text{ if $ i \ne j$ }
    \end{cases}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
    For example,
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
            \end{BMAT}\right]    
            \mapsto 
            \left[\begin{array}{rr}
                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2 - A_{21}^1  \\
                -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
            \end{array}\right]\,. 
    \]
    % For example, the $A$ above will define 
    % \acom{the transpose of! TODO. Had script?}
    % \[
    % \begin{bmatrix}
    %     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
    %     & t^2 \\
    %     & & t \\
    %     & & & t 
    % \end{bmatrix}    
    % \]
    % 
    % \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
    % \acom{Ok.}
    % 
    \begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
    $$
    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}\,. 
    $$
    \end{definition}
    So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).

>>>>

For $ s \ne 0$, we see that the equalities in $ z(s) $ reproduce the permutation $ p$, that $ r = 2 $, and that
\begin{equation} 
    \label{eq:rcols}
\begin{split}
        r_{z(s), 1}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda' \\
        r_{z(s), 2}(i) &=  N - \#\text{~boxes in first $i$ columns of }\lambda'' \,. 
\end{split}
\end{equation}
On the other hand, for $z(0)$, we get that $ r = 1$ and that 
\begin{equation} \label{eq:rcol2}
r_{z(0),1}(i) = r(i) = 
 N - 
     \#\text{~boxes in first $i$ columns of }\lambda\,. 
\end{equation}
\jcom{Someone should check that I chose the notation correctly to make this work out.}

\acom{What do we mean by equalities in $z(s)$ reproduce $p$? I thought $z(s)$ was defined by $p$. Also, $r_{z(s),1}(i) = N- r(p(k_1)) + r(p(k_1 + i)) = N - (N-\#\text{boxes in first }p(k_1)\text{ cols} + \cdots)\ne $~\Cref{eq:rcols}. We want to apply $p$ to $\{1,\dots,i\}$ and not just $i$. I guess we could clarify/declare that $r(p(i)) = N - \#$ boxes in columns $p(1),\dots,p(i)$. For a minute I thought it was actually fine, but what we have is: $r_{z(s),j}(i) = N - (\#\text{boxes in cols }1,\dots,p(k_j + i) - \#\text{boxes in cols }1,\dots,p(k_j))$ and what we want is $\dots (\#\text{boxes in cols }p(1),\dots,p(k_j + i) - \#\text{boxes in cols }p(1),\dots,p(k_j + i))$ right?}

@@

    In words, $A$ is a $\mu$ Jordan form matrix plus a $\mu\times\mu$ block matrix with possibly nonzero entries occuring in the first $\min(\mu_i,\mu_j)$ columns of the last row of each $\mu_i\times\mu_j$ block. 
    % $\dim \TT_\mu = N^2 - \dim \OO_\mu$. 
    In pictures, and by example, the elements $A$ for $\mu=(3,2,2,1)$ look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c;c}{ccc;cc;c;c}
             & 1 & & & & & \\
             &  & 1 & & & & \\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2 & A_{13}^1 & A_{14}^1 \\
              &  & &  & 1 & & \\
              A_{21}^1 & A_{21}^2 & & A_{22}^1 & A_{22}^2 & A_{23}^1 & A_{24}^1 \\
             A_{31}^1 & & & A_{32}^1 & & A_{33}^1 & A_{34}^1 \\
             A_{41}^1 & & & A_{42}^1 & & A_{43}^1 & A_{43}^1
        \end{BMAT}
        \right]\,. 
    \]
    % 
     To each $ A \in \TT_\mu$, we will associate the $m\times m$ matrix 
    of polynomials 
    $ g(A) = \left( g(A)_{ij} \right)$ in $ M_m(\CC[t]) $ as follows.
    \begin{equation}
        \label{eq:mvyofa}
        g(A)_{ij} = 
    \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i = j \\
            % \text{ if $ i = j$} \\
            - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} & i \ne j
        %  \text{ if $ i \ne j$ }
    \end{cases}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
    For example,
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            A_{11}^1 & A_{11}^2 & A_{11}^3 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            A_{21}^1 & A_{21}^2 & 0 & A_{22}^1 & A_{22}^2
            \end{BMAT}\right]    
            \mapsto 
            \left[\begin{array}{rr}
                t^{3} - A_{11}^3 t^2 - A_{11}^2 t - A_{11}^1 & -A_{21}^2t - A_{21}^1  \\
                -A_{12}^2 t - A_{12}^1 & t^{2} - A_{22}^2 t - A_{22}^1
            \end{array}\right]\,. 
    \]
    % For example, the $A$ above will define 
    % \acom{the transpose of! TODO. Had script?}
    % \[
    % \begin{bmatrix}
    %     t^3 - A_{11}^1 - A_{11}^2 t - A_{11}^3 t^2 & - A_{12}^1 - A_{12}^2 t & -A_{13}^1 & -A_{14}^1 \\
    %     & t^2 \\
    %     & & t \\
    %     & & & t 
    % \end{bmatrix}    
    % \]
    % 
    % \jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}
    % \acom{Ok.}
    % 
    \begin{definition} The ``\textbf{upper-triangular}'' \mvy slice $\UU^{\mu', \mu''}_{0,\AA}\rightarrow \AA $, defined by
    $$
    \UU^{\mu', \mu''}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu'_{i}} (t-s)^{\mu''_{i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}\,. 
    $$
    \end{definition}
    So a matrix in $\UU^{\mu', \mu''}_{0,\AA}$ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu'_{i}} (t-s)^{\mu''_{i}}$ ($i=1,\dots,m$).
